Stochastic blockmodeling of relational event dynamics

### 2012-06-01 docs/experiments.tex
Final NIPS submission.

Figure \ref{fig:parmats} uses a fitted model to provide an example of the differences in the dynamics that can exist between two groups of dyads with similar rate of occurrence.
We focus on the interactions between members of block 1 to members of block 3; 179 events occurred originating from a member of group 3 and 178 originated from group 1.
For this example we fit a model with an intercept $s_0$, $\texttt{ab-ba}$ effects $s_1$, and $\texttt{ab-by}$ effects $s_3$.
The two panels on the left show the variation in $s_0(t_M,i,j,\mathcal{A}_t)$, $s_1(t_M,i,j,\mathcal{A}_t)$ and $s_3(t_M,i,j,\mathcal{A}_t)$ across the dyads $(i,j)$ in blocks $(1,3)$ and $(3,1)$, respectively.
The boxplots on the right describe the posterior samples of the corresponding parameters $\beta_{1,3,p}$ and $\beta_{3,1,p}$.
Under the model, events from group 3 to group 1 occur roughly $e^1$ times as often.
Similarly, block (3,1) has a higher propensity for \texttt{ab-by} transitions under the model.
The model has learned that this structure exists in the data and our inferences from the parameter estimates are sensible given the observed statistics.

>>>>

Figure \ref{fig:parmats} uses a fitted model to provide an example of the differences in the dynamics that can exist between two groups of dyads with similar rate of occurrence.
We focus on the interactions between members of block 1 to members of block 3; 179 events occurred originating from a member of group 3 and 178 originated from group 1.
For this example we fit a model with an intercept $s_0$, $\texttt{ab-ba}$ effects $s_1$, and $\texttt{ab-by}$ effects $s_3$.
The two panels on the left show the variation in $s_0(t_M,i,j,\mathcal{A}_t)$, $s_1(t_M,i,j,\mathcal{A}_t)$ and $s_3(t_M,i,j,\mathcal{A}_t)$ across the dyads $(i,j)$ in blocks $(1,3)$ and $(3,1)$, respectively.
The boxplots on the right describe the posterior samples of the corresponding parameters $\beta_{1,3,p}$ and $\beta_{3,1,p}$.
Under the model, events from group 3 to group 1 occur roughly $e^1$ times as often.
Similarly, block (3,1) has a higher propensity for \texttt{ab-by} transitions under the model.
The model has learned that this structure exists in the data, and furthermore our inferences from the parameter estimates are sensible given the observed statistics.
